% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% The specifications of that environment should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{Internships}
\begin{itemize}

\item \begin{project}{Research Intern, NYU Tandon}{May '19 -- July '19}{Prof.\ Paweł Korus, Prof.\ Nasir Memon}%chktex 8
    \item Researched robust image hashes that are immune to typical image transformations, while being sensitive to malicious image edits such as face swaps, deep fakes, object addition/deletion.
    \item Constructed models that take an image and output a binary hash that would give lower \href{https://en.wikipedia.org/wiki/Hamming\_distance}{\textit{Hamming distances}} for hashes of similar images while giving more considerable distances for dissimilar images.
    \item Developed a \textit{framework} for testing against transformations like compression, contrast changes, blurring, warping.
    \item Trained various novel network architectures on the \href{https://dl.acm.org/citation.cfm?id=1756042}{\textit{triplet loss}} along with \href{https://arxiv.org/abs/1503.03832}{\textit{mining}} of examples for improved training.
    \item Tested the networks against \textit{adversarial attacks} such as \href{https://arxiv.org/abs/1412.6572}{\textit{FGSM}}, \href{https://arxiv.org/abs/1706.06083}{\textit{Projected Gradient Descent}}, \href{https://arxiv.org/abs/1712.04248}{\textit{Boundary Attack}}.
\end{project}

\item \begin{project}[https://github.com/rharish101/Plasticity-Networks]{Research Intern (Remote), NYU Tandon}{May '18 -- July '18}{Prof.\ Yao Wang}%chktex 8
    \item Researched \href{https://arxiv.org/abs/1804.02464}{\textit{differentiable plasticity}} for \textit{domain transfer} in images using Convolutional Neural Networks.
    \item Tested three architectures on the \textit{Street View House Numbers (SVHN)} dataset: standard ResNet, ResNet with plasticity on the fully-connected layer and ResNet with plasticity on all layers, using 20 and 56 layer variants.
    \item Improved \textit{efficiency} in the temporal update rule for the \textit{Hebbian weights} by using \href{http://www.matthewzeiler.com/pubs/cvpr2010/cvpr2010.pdf}{\textit{transpose convolution}}.% for convolutional layers.
    \item Achieved notable improvement in classification accuracy for the 20 layer models using full plasticity, when adapting models trained on the SVHN dataset for the MNIST dataset.
\end{project}

\item \begin{project}{Intern, Machine Learning Team, New York Office of IIT Kanpur}{May '17 -- July '18}{Prof.\ Manindra Agrawal}%chktex 8
    \item Developed an \textit{online} text clustering model using a \href{https://github.com/cloudwalkio/ddbscan}{fully-online modification} of the \textit{DBSCAN} algorithm.
    \item Implemented an \textit{online} document vectorisation model based on the \href{https://arxiv.org/abs/1405.4053}{\textit{Distributed Memory paragraph vectors}} model.
    \item Developed a \href{https://arxiv.org/abs/1301.3781}{\textit{Word2Vec}} model to identify duplicate documents using \href{http://proceedings.mlr.press/v37/kusnerb15.html}{\textit{Word Mover's Distance}} on word vectors.
    \item Trained a Convolutional Neural Network with sliding windows for English Optical Character Recognition (OCR).
\end{project}

\end{itemize}
