% SPDX-FileCopyrightText: 2019 Harish Rajagopal <harish.rajagopals@gmail.com>
%
% SPDX-License-Identifier: GPL-3.0-or-later

% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% The specifications of that environment should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{Practical Experience}
\begin{itemize}

\item \begin{project}{Software Engineer}{Feb '23 -- Present}{INTRASOFT AG}%chktex 8
    \iffull {
        \item \textbf{Led} the rewrite of the website \& customer portal, using the \href{https://processwire.com/}{ProcessWire} CMS with PHP, TypeScript, and \href{https://getuikit.com/}{UIkit}.
    }
    \item Implemented a \textbf{webshop} for managing online subscriptions\iffull{, payments}, discounts, and cancellations for a SaaS product.
    \item Created a \textbf{SAML single-sign-on\iffull{ service}} using SimpleSAMLphp and integrated it with the ProcessWire website.
    \item \textbf{Self-hosted an LLM} using \href{https://docs.vllm.ai}{vLLM}, integrating it into our main product through the OpenAI API.
    \item Developed distributed and configurable \textbf{load testing} using the \href{https://locust.io/}{Locust framework} for Python\iffull{, driven by Powershell scripts}.
\end{project}

\item \begin{project}{Research Intern}{May '19 -- Jul '19}{\iffull{Prof.\ Paweł Korus, Prof.\ Nasir Memon, }New York University}%chktex 8
    \item Researched \textbf{robust image hashes} that are immune to typical image transformations,\iffull{ measured by \href{https://en.wikipedia.org/wiki/Hamming\_distance}{Hamming distances},} while being sensitive to malicious image edits such as face swaps,\iffull{ object addition/deletion,} \& deep fakes.
    \item Developed a framework for testing against\iffull{ transformations like} compression, contrast changes,\ifsingle{ gamma,} blurring, warping.
    \iffull{
        \item Trained models on the \href{https://dl.acm.org/citation.cfm?id=1756042}{\textbf{triplet loss}} along with \href{https://arxiv.org/abs/1503.03832}{mining} of examples for improved training.
        \item Tested networks against \textbf{adversarial attacks} like \href{https://arxiv.org/abs/1412.6572}{FGSM}, \href{https://arxiv.org/abs/1706.06083}{Projected Gradient Descent}, \href{https://arxiv.org/abs/1712.04248}{Boundary Attack}.
    }
\end{project}

\item \begin{project}[https://github.com/rharish101/Plasticity-Networks]{Research Intern (Remote)}{May '18 -- Jul '18}{\iffull{Prof.\ Yao Wang, }New York University}%chktex 8
    \item Researched \href{https://arxiv.org/abs/1804.02464}{differentiable plasticity} for \textbf{domain transfer} in images using convolutional neural networks.
    \item Simplified the temporal update rule for the Hebbian weights of convolutional layers.
    \iffull{
        \item Tested various ResNet-based architectures on the Street View House Numbers (SVHN) dataset.
        \item \textbf{Improved accuracy}\iffull{ for smaller models} using plasticity, when adapting models pre-trained on\ifsingle{ the} SVHN\ifsingle{ dataset} for MNIST.\@
    }
\end{project}

\item \begin{project}{Intern, Machine Learning Team}{May -- Jul, 2017 \& 2018}{NYC Office of IIT Kanpur}%chktex 8
    \item Developed an \textbf{online text clustering} model using a \href{https://github.com/cloudwalkio/ddbscan}{fully-online modification} of the DBSCAN algorithm.
    \iffull{
        \item Implemented an \textbf{online document vectorisation} model using \href{https://arxiv.org/abs/1405.4053}{Distributed Memory paragraph vectors}.
    }
    \item Developed a \href{https://arxiv.org/abs/1301.3781}{Word2Vec} model to identify duplicate documents using \href{http://proceedings.mlr.press/v37/kusnerb15.html}{Word Mover's Distance} on word vectors.
\end{project}

\end{itemize}
